Response to reviewers

### 2022-02-16 response/response1.Rmd
response

XXX We need to review this literature. It's not true that we have ignored it, the main reference is Dasu! But we need to decide whether there is more that we shoudl cite.

Outlier detection ???

@@

* We have fixed the sentences and the reference. XXX Which one?

>>>>

We agree that there is substantial literature on data cleaning. We have referenced one of the main works, Dasu and Johnson (2003) but don't feel it is necessary to cite more than this. We have similarly only pointed to one main reference for IDA and EDA.

@@

* We have fixed the sentences and the reference.
